Fourier-domain modulations and delays of gravitational-wave signals

### 2018-06-18 docs/paper_method.tex
Tiny addition to abstract.

We present a Fourier-domain based approach modulations and delays of gravitational wave signals, a problem which arises in two different contexts. For space-based detectors like LISA, the orbital motion of the detector introduces a time-dependency in the response of the detector, consisting of both a modulation and a varying delay. In the context of signals from precessing spinning binary systems, a useful tool for building models of the waveform consists in representing the signal as a time-dependent rotation of a quasi-non-precessing waveform. In both cases, being able to compute transfer functions for these effects directly in the Fourier domain may enable performance improvements for data analysis applications by using fast frequency-domain waveforms. Our results generalize previous approaches based on the stationary phase approximation for inspiral signals, extending them by including delays and computing corrections beyond the leading order, while being applicable to the broader class of signals of inspiral-merger-ringdown waveforms. In the LISA case, we find that a leading-order treatment is accurate for high-mass and low-mass signals that are chirping enough, with reconstruction errors that can be reduced by consistently including the corrections we derived. By contrast, low-mass binary black holes, if far away from merger and slowly-chirping, cannot be handled by our perturbative formalism and we develop another approach for these systems. In the case of precessing binaries, we perform a limited exploration of the merger-ringdown range based on a toy model for the precession. We find that, depending on the post-merger frame velocity, deviations from leading order can become qualitatively large to the point of challenging our perturbative formalism, while affecting mainly subdominant mode contributions and giving rise to a limited unfaithfulness in the full waveform. Including higher-order corrections consistently reduces the unfaithfulness, and we further develop an alternative approach to accurately represent post-merger features.

>>>>

We present a Fourier-domain based approach modulations and delays of gravitational wave signals, a problem which arises in \jgb{at least} two different contexts. For space-based detectors like LISA, the orbital motion of the detector introduces a time-dependency in the response of the detector, consisting of both a modulation and a varying delay. In the context of signals from precessing spinning binary systems, a useful tool for building models of the waveform consists in representing the signal as a time-dependent rotation of a quasi-non-precessing waveform. In both cases, being able to compute transfer functions for these effects directly in the Fourier domain may enable performance improvements for data analysis applications by using fast frequency-domain waveforms. Our results generalize previous approaches based on the stationary phase approximation for inspiral signals, extending them by including delays and computing corrections beyond the leading order, while being applicable to the broader class of signals of inspiral-merger-ringdown waveforms. In the LISA case, we find that a leading-order treatment is accurate for high-mass and low-mass signals that are chirping enough, with reconstruction errors that can be reduced by consistently including the corrections we derived. By contrast, low-mass binary black holes, if far away from merger and slowly-chirping, cannot be handled by our perturbative formalism and we develop another approach for these systems. In the case of precessing binaries, we perform a limited exploration of the merger-ringdown range based on a toy model for the precession. We find that, depending on the post-merger frame velocity, deviations from leading order can become qualitatively large to the point of challenging our perturbative formalism, while affecting mainly subdominant mode contributions and giving rise to a limited unfaithfulness in the full waveform. Including higher-order corrections consistently reduces the unfaithfulness, and we further develop an alternative approach to accurately represent post-merger features.
